Robots, Are They Overlords or Serf-Laborers?

### 2015-06-13 draft1.tex
Edit abstract

% plagiarism check
% cohesion check
% grammar check (firt two page of new paper)
\documentclass[man]{apa6}
\title{Robots, Are They Overlords or Serf-Laborers?}
\author{Murat Ambarkutuk}
\affiliation{English Language Institute, University of Delaware \\ murata@udel.
edu}
\note{First Draft; 6/8/2015; \LaTeX}
\usepackage{apacite}
% modify it!
\abstract{Of all the tools and methods invented by humankind to tame nature and make use of its challenges, the invention of computer has had the greatest impact on society.
 Coupled with the Internet, computers have changed the way billions of humans work, entertain themselves, and think.
 Since the rise of the computers, Artificial Intelligence (AI) has been one of the most debated issues in the field of engineering.
 Research toward the creation of AI includes a creation of self-aware machines that have superior intellectual abilities to that of human abilities.
 However, many researchers argue that the creation of AI will deeply change the society and it will help humankind to solve major societal problems, while others refute the arguments for the conceptual invention because of ethical problems that AI will bring such as an anticipated human annihilation by these agents.
 This paper focuses on the the ethical problems that the creation of AI will raise.
}
\keywords{artificial intelligence, robotics, ethics, society} 
\shorttitle{Overlords vs. Serf-Laborers}
\leftheader{Even-Numbered Page Header} %Change it
\begin{document}
\maketitle

\section{Introduction}
Even though the term robot was coined two centuries ago and the idea of AI emerged decades ago, some of the problems that have been raised by these two terms are yet to be solved.
Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details.
Thus, this paper focuses on numerous definitions for these concepts and their various applications which create intricacies and challenges in many level, varying from individual to societal level.
The formation of this paper is as follows: First section will emphasize on the issues that robotics have arisen; the second and third section then scrutinize the definitions and applications of robots; respectively in order to locate the roots of these issues and intricacies.

>>>>

% plagiarism check
% cohesion check
% grammar check (firt two page of new paper)
\documentclass[man]{apa6}
\title{Robots, Are They Overlords or Serf-Laborers?}
\author{Murat Ambarkutuk}
\affiliation{English Language Institute, University of Delaware \\ murata@udel.
edu}
\note{First Draft; 6/8/2015; \LaTeX}
\usepackage{apacite}
% modify it!
\abstract{Of all the tools and methods invented by humankind to tame nature and make use of its challenges, the invention of computer has had the greatest impact on society.
 Coupled with the Internet, computers have changed the way billions of humans work, entertain themselves, and think.
 Since the rise of the computers, Artificial Intelligence (AI) has been one of the most debated issues in the field of engineering.
 Research toward robotics is also based upon the creation of AI that will run the robots thanks to superior cognitive and perceptive abilities of AI than that of man. 
 However, many researchers argue that the creation of AI will deeply elevate society and it will help humankind to solve major societal problems, while others refute the arguments for that conceptual invention because of ethical problems that AI will bring.
 This paper explores the ethical problems that the creation of AI will raise, and it attribute these problems resulted from widely varying definitons and the applications of these .
}
\keywords{artificial intelligence, robotics, ethics, society} 
\shorttitle{Overlords vs. Serf-Laborers}
\leftheader{Even-Numbered Page Header} %Change it
\begin{document}
\maketitle

\section{Introduction}
Even though the term robot was coined two centuries ago and the idea of Artificial Intelligence (AI) emerged decades ago, some of the problems that have been raised by these two terms are yet to be solved.
Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details.
Thus, this paper focuses on numerous definitions for these concepts and their various applications which create intricacies and challenges in many level, varying from individual to societal level.
The formation of this paper is as follows: First section will emphasize on the issues that robotics have arisen; the second and third section then scrutinize the definitions and applications of robots; respectively in order to locate the roots of these issues and intricacies.
